---
title: "Psychology of Swearing"
author: "Emily Nordmann"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(lsr)
library(gridExtra)
library(ggforce)
library(afex)
library(emmeans)
dat <- read_csv("data.csv")
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
dat2 <- rename(dat,
              age = `Age (in whole years)`,
              gender = Gender,
              letter = `Please write as many words as you can beginning with the letter "A".`, 
              animal = `Please write down as many different types of animal as you can.`,
              swears = `Please write down as many swear words as you can.`) %>%
  select(-Timestamp) %>%
  mutate(subject = row_number()) %>%
  mutate(age = as.numeric(age),
         gender = as.factor(gender),
         subject = as.factor(subject)) %>%
  select(subject,everything()) %>%
  mutate(gender = fct_relevel(gender, c("Man", "Woman", "Other")))
  

# convert to tidytext and calculate number of words in each category

dat_letter <- dat2 %>%
  select(subject, letter) %>%
  unnest_tokens(input = letter, output = words) %>%
  mutate(type = "letter")
 

dat_animal <- dat2 %>%
  select(subject, animal) %>%
  unnest_tokens(input = animal, output = words) %>%
  mutate(type = "animal")

dat_swears <- dat2 %>%
  select(subject, swears) %>%
  unnest_tokens(input = swears, output = words) %>%
  mutate(type = "swear")

all_dat <- bind_rows(dat_animal, dat_letter, dat_swears)

all_counts <- all_dat %>%
  group_by(subject, type) %>%
  summarise(score = length(words)) %>%
  inner_join(dat2, by = "subject") %>%
  select(subject:gender) %>%
  ungroup()

```

## Relationship between age and vocabulary


```{r, echo = FALSE}
corr_dat <- as.data.frame(all_counts %>%
  spread(key = type, value = score) %>%
    select(age, animal, swear))

vocab_corr <- correlate(corr_dat, test = TRUE, p.adjust.method = "holm")

```

The correlation between age and animals is r = `r vocab_corr$correlation[1,2] %>% round(2)`, p = `r vocab_corr$p.value[1,2] %>% round(3)`. 

The correlation between age and swears is r = `r vocab_corr$correlation[1,3] %>% round(2)`, p = `r vocab_corr$p.value[1,3] %>% round(3)`. 

The correlation between swears and animals is r = `r vocab_corr$correlation[3,1] %>% round(2)`, p = `r vocab_corr$p.value[3,1] %>% round(3)`. 

```{r, echo = FALSE}
ggplot(corr_dat) +
  geom_point(aes(x = .panel_x, y = .panel_y)) +
  geom_autodensity() +
  facet_matrix(vars(age, animal, swear), layer.diag = 2) +
  theme_bw()
```


## Swearing scores by gender

```{r, echo=FALSE}
all_counts %>%
  filter(type == "swear") %>%
  group_by(gender) %>%
  summarise(average_score = mean(score, na.rm = TRUE)) %>%
  knitr::kable(align = 'c', digits = 2)  

```

<br>

```{r, echo = FALSE}
all_counts %>%
  filter(type == "swear") %>%
  ggplot(aes(x = gender, y = score, fill = gender)) +
  geom_violin(trim = FALSE, alpha = .5) +
  geom_boxplot(show.legend = FALSE, alpha = .7, width = .2) +
  theme_minimal() +
  scale_fill_viridis_d(option = "E")
```

```{r, echo = FALSE, message=FALSE}
anova_dat <- all_counts %>%
  filter(type == "swear") %>%
  droplevels()

mod <- aov_ez(id = "subject",
       dv = "score",
       between = "gender",
       data = anova_dat)

mod_pairwise <-emmeans(mod$aov, pairwise ~ gender, adjust = "bonferroni")
mod_contrasts <- mod_pairwise$contrasts %>% tidy()

mod$Anova %>%
  knitr::kable(align = 'c', digits = 2) 

mod_contrasts %>%
  knitr::kable(align = 'c', digits = 2) 
```



## Most frequent swear words

```{r, echo = FALSE}
dat_swears%>%
  na.omit()%>%
  count(words, sort = TRUE)%>%
  head(10) %>%
  mutate(words = reorder(words, n))%>%
  ggplot(aes(x = words, y = n, fill = words))+
  geom_col(show.legend = FALSE)+
  coord_flip() +
  scale_fill_viridis_d(option = "D")
```


